Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-09 main.tex
rough draft for first part of intro

    %%% CONTEXT %%%
    Data analysis on massive data sets (stemming from areas such as genomics, 
    remote sensing, or biomedical imaging -- to name just a few) has become ubiquitous in science;
    it often happens in the form of workflows, \iec separate software components chained together
    in some kind of complex pipeline~\cite{DBLP:journals/dbsk/LeserHDEGHKKKKK21}.
    Such workflows are usually represented as directed acyclic graphs (DAGs).
    The DAG vertices represent the software components (more general: the workflow \emph{tasks}),
    while the edges model I/O dependencies between the tasks~\cite{adhikari2019survey,liuPacitti}.
    Large workflows with resource-hungry tasks can easily exhaust the capabilities of a 
    single computer and are thus executed on a parallel or distributed platform.
    An efficient execution of the workflows on such platforms requires not only to map the tasks
    to a particular processor, but also a good task schedule, \iec an execution order
    and possibly also starting times for the tasks.

    \begin{itemize}
      \item This also allows to reuse processors, which is important to achieve good HW utilization / makespans (explain!).
    \end{itemize}

    %%% MOTIVATION %%%
    \begin{itemize}
      \item Heterogeneous means: different CPU speeds, different mem sizes
      \item With different mem sizes: more difficult to adhere to mem constraints
      \item Adhering to memory constraints is very important to avoid execution failures.
      \item In this paper, we formulate the problem that takes memories into consideration (using (nearly the) model from ICPP paper)
      \item HEFT (see book chapter) is one of the most popular heuristics (cite a review).
      \item However, existing HEFT variations do not take memory sizes into consideration (\skug{check in related work if true!}).
        Note: 2 papers that deal with memory sizes, but model is very different!
      \item Many scheduling strategies assume that task running times provided to them are accurate. This is not really the case
        in practice. Thus, one needs to adapt the schedule when major deviations occur (which is the case in practice).
        List-based schedulers such as HEFT are not designed for adaptation and would compute a completely schedule from scratch.
    \end{itemize}

>>>>

    %%% CONTEXT %%%
    Data analysis on massive data sets (stemming from areas such as genomics, 
    remote sensing, or biomedical imaging -- to name just a few) has become ubiquitous in science;
    it often happens in the form of workflows, \iec separate software components chained together
    in some kind of complex pipeline~\cite{DBLP:journals/dbsk/LeserHDEGHKKKKK21}.
    Such workflows are usually represented as directed acyclic graphs (DAGs).
    The DAG vertices represent the software components (more general: the workflow \emph{tasks}),
    while the edges model I/O dependencies between the tasks~\cite{adhikari2019survey,liuPacitti}.
    Large workflows with resource-hungry tasks can easily exhaust the capabilities of a 
    single computer and are thus executed on a parallel or distributed platform.
    An efficient execution of the workflows on such platforms requires to map the tasks
    to a particular processor; to increase utilization by reusing finished processors,
    one also needs a task schedule, \iec a valid execution order that respects the dependencies
    and possibly also starting times for the tasks.

    %%% MOTIVATION %%%
    \begin{itemize}
      \item Heterogeneous means: different CPU speeds, different mem sizes
      \item With different mem sizes: more difficult to adhere to mem constraints
      \item Adhering to memory constraints is very important to avoid execution failures.
      \item In this paper, we formulate the problem that takes memories into consideration (using (nearly the) model from ICPP paper)
      \item Objective: makespan (proxy for total execution time)
      \item HEFT (see book chapter) is one of the most popular heuristics (cite a review).
      \item However, existing HEFT variations do not take memory sizes into consideration (\skug{check in related work if true!}).
        Note: 2 papers that deal with memory sizes, but model is very different!
      \item Many scheduling strategies assume that task running times provided to them are accurate. This is not really the case
        in practice. Thus, one needs to adapt the schedule when major deviations occur (which is the case in practice).
        List-based schedulers such as HEFT are not designed for adaptation and would compute a completely schedule from scratch.
    \end{itemize}
